### 2018-04-25 papers/synth/encoding.tex
pape

In this section we will present a list of problems that may arise from
synthesis of VTSs from partial available information.

@@

Our objective is to find missing parts of a partially known VTSs.
%
We will consider several variations of the problem.
%
\begin{itemize}
\item Learning activity functions
\item Modifying labels of the nodes and edges
\item Adding missing edges
\item Adding
\end{itemize}

@@

The missing information can be in any of these combinations parts of VTS. For example existence of some undiscovered edges or nodes, or insufficient knowledge about the presence of molecules in some part of the VTS (either on the node or on the edge). To cover most of the likely variations of this missing information we have encoded the following variants of VTS synthesis.
%
%
\begin{enumerate}[label=\Alph*]
\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
\item  Modify the flow of molecules on the nodes and on the edges.
  \begin{enumerate}
  	\item use available set of molecules.
    \item allow new molecule type to be added.     
  \end{enumerate}        
\item Learning meaningful activity function. 
  \begin{enumerate}
    \item kcnf: low depth circuit.
    \item Boolean gates: And, Or.
    \item Boolean gates with linear combination.  
    \end{enumerate}        
  % - Function dependence with var occurring once.
\item  VTS repair. [Allow both delete and add to the system]
\end{enumerate}

\begin{align}
  \exists n_{i_k} \, a_{i_k} \, e_{ijqk} \, b_{ijqk} \, p_{k_{k^{-}}} \,  r_{i_j} \, 
               ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
  \tag{E1}\label{eq:addedge1}
\end{align}

>>>>

In this section, we will present a list of problems that may arise from
synthesis of VTSs from partial available information
and our method for completing the missing parts.

@@

We will assume that we are given a VTS, whose all components
are not specified.
%
Our objective is to find the missing parts.
%
The missing information can be in any of these combinations parts of
VTS. For example existence of some undiscovered edges or nodes, or
insufficient knowledge about the presence of molecules in some part of
the VTS (either on the node or on the edge).
%
To cover most of the likely variations of this missing information we
have encoded the following variants of VTS synthesis.

% % We will consider several variations of the problem.
% %
% \begin{itemize}
% \item Learning activity functions
% \item Modifying labels of the nodes and edges
% \item Adding missing edges
% \item Adding 
% \end{itemize}

@@

%
%
\begin{enumerate}[label=\Alph*]
\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
\item  Modify the flow of molecules on the nodes and on the edges.
  \begin{enumerate}
  	\item use available set of molecules.
    \item allow new molecule type to be added.     
  \end{enumerate}        
\item Learning meaningful activity functions from a given language of
  propositional formulas
  \begin{enumerate}
    \item kcnf: low depth circuit.
    \item Boolean gates: And, Or.
    \item Boolean gates with linear combination.  
    \end{enumerate}        
  % - Function dependence with var occurring once.
\item  VTS repair. [Allow both delete and add to the system]
\end{enumerate}

\begin{align}
  \exists n, a, e, b, p, r, p,
  ( \texttt{Consistancy}\land \texttt{ActiveNode} \land 
  \texttt{ActiveEdge} \land \texttt{GivenCons} \land
  \texttt{ModifyCons} )   
  \tag{E1}\label{eq:addedge1}
\end{align}

% \begin{align}
%   \exists n_{i_k} \, a_{i_k} \, e_{ijqk} \, b_{ijqk} \, p_{k_{k^{-}}} \,  r_{i_j} \, 
%                ( basic_vts_constraints \land  vts\_activity\_constraint \land  given\_vts\_information \land  restriction\_on\_modification )   
%   \tag{E1}\label{eq:addedge1}
% \end{align}

### 2018-04-25 papers/synth/intro.tex
pape

% Describe VTS in detail
While VTSs transports molecules, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
Both the molecules must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} molecules and analogously
the channel is considered to be {\em fused} with the
destination compartment.
%
Not all the pairs of molecules can participate in the fusion, it is
usually determined by wet experiments the potential fusion pairs.
%
To ensure effective regulation, the fusing molecule pairs must be
unique for each fused channel-compartment pair.
%
A molecule that have participated in a fusion must not interfere
with fusion at different compartments or channels.
%
Therefore, the molecule must be inactive in appropriate compartments.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecule in a compartment or
channel may make the active or inactive.
%
We call this regulation as {\em activity functions}.

% Defending our model
%
In the VTS model, we assume that the system is in study state and
the concentrations of the molecules in the compartments do not change over time.
%
We model the system as a labelled graph, where compartments are nodes and
transport channels are edges.
%
The set of molecules present and their activity in a compartment or
a channel is the label of the respective node or edge.
%
The regulation controls are defined by a fusion pairing matrix
containing Boolean values for each pair of molecules and activity
Boolean functions.
%
Since the system is in study state, we expect that any molecule that
leaves a compartment must come back via some path on the graph.
%
We call this property of VTS as {\em stability}.

% Partial info defence
%
Although the VTSs are important, our understanding of VTSs are partial.
%
It largely means the patch work of wet experiments~\cite{model} for
identifying the compartments, channels, molecules, their activity, and
regulatory control.
%
Often the information is scattered around in several publications.
%
Even after with some effort we may collate all the known information about
a VTS, we may still have unknown pieces of the system.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
For example, we may suspect that some edges are missing in a VTS that
does not satisfy the stability condition.
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%

>>>>

% Describe VTS in detail
While VTSs transports molecules, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
Both the molecules must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} molecules and analogously
the channel is considered to be {\em fused} with the
destination compartment.
%
Not all the pairs of molecules can participate in the fusion, the
potential fusion pairs are usually determined by wet experiments.
%
To ensure effective regulation, the fusing molecule pairs must be
unique for each fused channel-compartment pair.
%
A molecule that have participated in a fusion must not interfere
with fusion at different compartments or channels.
%
Therefore, the molecule must be inactive in appropriate compartments.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecule in a compartment or
channel may make the active or inactive.
%
We call this regulation as {\em activity functions}.

% Defending our model
%
In the VTS model, we assume that the system is in study state and
the concentrations of the molecules in the compartments do not change over time.
%
We model the system as a labelled graph, where compartments are nodes and
transport channels are edges.
%
The set of molecules present and their activity in a compartment or
a channel is the label of the respective node or edge.
%
The regulation controls are defined by a fusion pairing relation
containing pairs of molecules and activity
Boolean functions.
%
Since the system is in study state, we expect that any molecule that
leaves a compartment must come back via some path on the graph.
%
We call this property of VTS as {\em stability}.

% Partial info defence
%
Although the VTSs are important, our understanding of VTSs are partial.
%
It largely means that the current knowledge is due to the patch work
of wet experiments~\cite{model} for identifying the compartments,
channels, molecules, their activity, and regulatory control.
%
Often the information is scattered around in several publications.
%
Even after with some effort we may collate all the known information about
a VTS, we may still have unknown pieces of the system.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
For example, we may suspect that some edges are missing in a VTS that
does not satisfy the stability condition.
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
